### 2021-04-08 papers/SYRCoSE/overview.tex

We build our mechanisation on top of \mathcomp~\cite{Mahboubi-Tassi:MATHCOMP17} library 
using the \ssreflect~\cite{Gonthier-al:SSR2016} extension of the \coq system.
We also use the \emph{small-scale reflection} 
methodology~\cite{Gonthier-Assia:SSR2010, Gonthier-al:SSR2016}, 
a key ingredient of the \ssreflect.

The small-scale reflection approach is based on 
pervasive use of symbolic representation of the proof goal, 
which \emph{reflects} the logical representation. 
The symbolic representation can be manipulated 
by the computational engine of the language, 
allowing the user to automate low-level routine 
proof management by using various decision 
and simplification procedures. 
Whenever the user needs to guide the proof 
it can switch to logical representation
and perform some proof steps manually.

To achieve better automation one is recommended 
to use \emph{decidable} and \emph{computable} procedures
whenever possible.
For example, in the context of our library, 
we encode the binary relations of the event structures
as decidable \texttt{bool}-valued relations, 
\ie $\caOrd, \cfRel : E \fun E \fun \texttt{bool}$,
as opposed to \emph{propositional} 
relations of type $E \fun E \fun \texttt{Prop}$.

>>>>

We build our mechanisation on top of the \mathcomp~\cite{Mahboubi-Tassi:MATHCOMP17} library 
using the \ssreflect~\cite{Gonthier-al:SSR2016} extension of the \coq system.
We also use the \emph{small-scale reflection} 
methodology~\cite{Gonthier-Assia:SSR2010, Gonthier-al:SSR2016}, 
a key ingredient of the \ssreflect.

The small-scale reflection approach is based on 
pervasive use of symbolic representations \emph{intermixed}
with logical ones within the confines of the same proof goal,
as opposed to large-scale reflection which does not allow such mixing.
Symbolic representations are connected to the corresponding logical ones
via user-defined \emph{reflect predicates}.
The symbolic representation can be manipulated 
by the computational engine of the language, 
allowing the user to automate low-level routine 
proof management by using various decision 
and simplification procedures.
Whenever the user needs to guide the proof 
it can switch to logical representation
and perform some proof steps manually.

To achieve better automation one is encouraged 
to use \emph{decidable} and \emph{computable} procedures
whenever possible.
For example, in the context of our library, 
we encode the binary relations of the event structures
as decidable \texttt{bool}-valued relations, 
\ie $\caOrd, \cfRel : E \fun E \fun \texttt{bool}$,
as opposed to \emph{propositional} 
relations of type $E \fun E \fun \texttt{Prop}$.
